\documentclass{IEEE_lsens}

\usepackage{cite}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{url}
\usepackage{textcomp}

\graphicspath{{../figures/}}

\begin{document}

\markboth{IEEE Sensors Letters}{Swami and Sonawane: Wire-Level Interrupt-to-Decision Latency of On-Sensor MLC versus Host Inference}

\IEEELSENSarticlesubject{Sensor System Integration, Intelligent Sensing}

\title{Wire-Level Interrupt-to-Decision Latency of On-Sensor MLC versus Host Inference on the NVIDIA Jetson Orin Nano: A Pre-Registered Measurement Study}

\author{\IEEEauthorblockN{Akul~Swami\IEEEauthorrefmark{1} and Dnyaneshwar~Sonawane\IEEEauthorrefmark{2}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Independent Researcher (e-mail: swami.akul@alumni.uml.edu)\\
\IEEEauthorrefmark{2}Independent Researcher (e-mail: dnyaneshwar.sonawane19@gmail.com)}
\thanks{Corresponding author: A. Swami (e-mail: swami.akul@alumni.uml.edu).}%
\thanks{Code, data, and the full pre-registration chain are available at https://github.com/akulswami/sensor-mlc-latency.}%
\thanks{This work has been submitted to the IEEE for possible publication. Copyright may be transferred without notice, after which this version may no longer be accessible.}}

\IEEELSENSmanuscriptreceived{Manuscript submitted May 28, 2026.}

\IEEEtitleabstractindextext{%
\begin{abstract}
\input{_abstract}
\end{abstract}

\begin{IEEEkeywords}
Inertial measurement unit, machine learning core, edge inference, latency measurement, pre-registration, LSM6DSOX.
\end{IEEEkeywords}}

\maketitle

\input{_body}

\begin{thebibliography}{1}

\bibitem{ref1} STMicroelectronics, ``LSM6DSOX: 6-axis IMU with machine learning core,'' Datasheet DS12140, 2024.

\bibitem{ref2} STMicroelectronics, ``LSM6DSOX: Machine Learning Core,'' Application Note AN5259, 2023.

\bibitem{ref3} M.~Razmi and I.~Shojaei, ``Event-driven on-sensor locomotion mode recognition using a shank-mounted IMU with embedded machine learning for exoskeleton control,'' arXiv:2602.21418, Feb.\ 2026.

\bibitem{ref4} A.~Swami, ``Pre-registration chain for the sensor-mlc-latency study,'' Zenodo, externally-timestamped multi-amendment DOI chain (v6.1--v7.11), 2026. doi:10.5281/zenodo.20437893 (v7.11).

\bibitem{ref5} H.~B.~Mann and D.~R.~Whitney, ``On a test of whether one of two random variables is stochastically larger than the other,'' \emph{Ann. Math. Statist.}, vol.~18, no.~1, pp.~50--60, 1947.

\bibitem{ref6} J.~L.~Hodges and E.~L.~Lehmann, ``Estimates of location based on rank tests,'' \emph{Ann. Math. Statist.}, vol.~34, no.~2, pp.~598--611, 1963.

\bibitem{ref7} D.~J.~Schuirmann, ``A comparison of the two one-sided tests procedure and the power approach for assessing the equivalence of average bioavailability,'' \emph{J. Pharmacokinet. Biopharm.}, vol.~15, no.~6, pp.~657--680, 1987.

\bibitem{ref8} S.~Holm, ``A simple sequentially rejective multiple test procedure,'' \emph{Scand. J. Statist.}, vol.~6, no.~2, pp.~65--70, 1979.

\bibitem{ref9} A.~Swami and N.~Chougule, ``Per-platform GPIO overhead in hardware-validated edge ML inference timing,'' arXiv:2605.02835, May~2026.

\end{thebibliography}

\end{document}
